\sysfull

### 2017-11-17 paper/systemdescription.tex
overview: whitespace
system description background
sec 4

\sys's programming interface, listed in Table~\ref{tab:viper_syntax}, consists of
constructs for defining tasks~\cite{chain,alpaca} and accessors for
protected variables shared between tasks. These anotations are added either by
the programmer (in the manual translation mode) or the compiler (in automatic
translation mode). As in prior task-based intermittent programming
models~\cite{chain,alpaca}, tasks are functions that are not allowed to have
any direct callers but receive control by explicit {\tt next\_task} statements.
In \sys, a task transition atomically commits the memory operations of the
current task.  The programmer identifies each task by adding the {\tt task}
keyword to the function's declaration and designates one task as the {\em
origin} task at which execution begins. After a power failure,
\sys restarts from the last (partially) executed task.
%
A \sys program manipulates {\em protected} state---accessed by more than one
task---using the \emph{read variable} ({\tt RVAR}) and \emph{write variable}
({\tt WVAR}) operations. These operations convey to \sys's memory manager which
data must be buffered in volatile memory and committed.

>>>>

\sys's programming interface, listed in Table~\ref{tab:viper_syntax}, consists of
constructs for defining tasks~\cite{chain,alpaca} and accessors for
protected variables shared between tasks. These annotations are added either by
the programmer (in the manual translation mode) or the compiler (in automatic
translation mode). As in prior task-based intermittent programming
models~\cite{chain,alpaca}, tasks are functions that are not allowed to have
any direct callers but receive control by explicit {\tt next\_task} statements.
In \sys, a task transition does not atomically commit the memory operations of the current task---commit is deferred until the boundary of the coalesced task is reached. The programmer identifies each task by adding the {\tt task}
keyword to the function's declaration and designates one task as the {\em
origin} task at which execution begins. After a power failure,
\sys restarts from the last (partially) executed coalesced task.
%
A \sys program manipulates {\em protected} state---accessed by more than one
task---using the \emph{read variable} ({\tt RVAR}) and \emph{write variable}
({\tt WVAR}) operations. These operations convey to \sys's memory manager which
data must be buffered in volatile memory and committed.
